### 2016-09-05 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
More

#Run the model
lm2 <- lmer(CqTelomere ~  LogAge+Tarsus + NonHelper + Sex + BodyMass  +yday + (1|FieldPeriodID) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

>>>>

#Run the model
lm2 <- lmer(RTL ~  LogAge+Tarsus + Helper + NonHelper + Sex + BodyMass  +yday + (1|FieldPeriodID) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging
